Object Categorization based on RGBD data

### 2014-01-02 Disseration/introduction.tex
dissertation update

	Capturing visual information of any kind have never been easier. Almost everyone of us posses a camera, be it a professional dSLR or a tiny one embedded into one of the ubiquitous smartphones. As human beings we have no difficulty understanding this data, just as we have no difficulty understanding what our eyes see. Unfortunately, the situation of our computers is the very opposite. Storage capacity of modern-day computers is overwhelming.  But even if hard-drives are full of images it is impossible to identify their semantic meaning without the aid of specialised algorithms, however. These algorithms often balance on the verge of image processing and machine learning --- they are a part of an area called computer vision. As Forsyth and Ponce \cite{ponce2011cv} have it: \begin{quote} computer vision is (...) an enterprise that uses statistical methods to disentangle data using models constructed with the aid of geometry, physics, and learning theory.\end{quote} The area of computer vision is not new. The original applications were industrial inspection or mobile robot navigation. More recent approaches consider problems such as human-machine interfaces, medical diagnostics, or image retrieval.

>>>>

	Capturing visual information have never been easier. Terabytes of photographs and movies are uploaded on the Web every day, causing unprecedented growth of popular storage services. The traditional means of annotation cease to suffice. Hand-tagging and description have strong cultural dependencies and introduce ambiguity. Without any better solution, databases become increasingly harder to navigate and browse. Matters could have been better if computers understood content they deal with. But even the latest software is far from and cannot be considered intelligent in general terms. On the other hand, an area of machine learning define routines for learning complex and strongly non-linear functions mapping an arbitrary input to a given set of outputs. This is how computer vision can be used to make sense of any visual content, provided that there is enough data. As Forsyth and Ponce \cite{ponce2011cv} have it:

	\begin{quote} 
		computer vision is (...) an enterprise that uses statistical methods to disentangle data using models constructed with the aid of geometry, physics, and learning theory.
	\end{quote}

	The area of computer vision is not new and have initially dealt with industrial inspection or mobile robot navigation. Recent applications include human-machine interfaces, medical diagnostics and image retrieval.
